Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-16 article/ms.tex
added K vs Mg plot and relevant files, begun discussion points

Stellar absorption spectra act as a record of the primordial conditions within which the star formed. Stars displaying unusual elemental abundances provide are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy. Stars with  depleted Mg and enhanced K abundances have thus far found only in two massive globular clusters: NGC 2419 and NGC 2808. The primordial origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of even stars with typical galactic values of K abundances. The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey. Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with anomalously depleted Mg and enhanced K abundances, though none with abundances comparable to the stars identified in NGC 2419.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{posterchildof13.png}
    \caption{Poster Child}
    \label{mhist}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{loggteffof113.png}
    \caption{Effective temperature, log surface gravity, metalicity}
    \label{mhist}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{globclustof113.png}
    \caption{Galactic coordinates for Mg-K stars and known globular clusters}
    \label{mhist}
\end{figure}

@@

>>>>

Stellar absorption spectra act as a record of the primordial conditions within which the star formed. Stars displaying unusual elemental abundances provide are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy. Stars with  depleted Mg and enhanced K abundances, measured as [Mg/Fe] and [K/Fe], have thus far only been found in the two massive globular clustersr NGC 2419 and NGC 2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of stars with typical galactic values of [K/Fe]. The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey. Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with anomalously depleted [Mg/Fe] and enhanced [K/Fe] abundances, though none with abundances comparable to the extreme population of stars identified in NGC 2419.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{posterchildof13.png}
    \caption{Poster Child}
    \label{posterchild}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{loggteffof113.png}
    \caption{Effective temperature, log surface gravity, metalicity}
    \label{tefflogg}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{globclustof113.png}
    \caption{Galactic coordinates for Mg-K stars and known globular clusters}
    \label{galcord}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMgab.png}
    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808.}
    \label{KvsMg}
\end{figure}

@@

\section{Discussion}

\begin{itemize}
\item Association with globular clusters: basically all stars (will have to redo plot and search for the new tables) are not associated with globular clusters. in terms of those which are kinda close in GC, state which cluster(s) they could be associated with. We lack dynamics information, but potentially the next data release from GAIA will help with that. Check with apparent magnitudes to see if the stars are consistent in that regard.

\item Metalicity: the candidate stars are found at a wide range of metalicities, from \todo{-1.4<[Fe/H]<0.3}. for comparison, NGC 2808 and NGC 2419 have [Fe/H] ~-2.

\item Abundances: K abundances are lower and Mg abundances are higher than those in the extreme population of 2419. however, they \textit{are} still (perhaps) significantly K enhanced and Mg depleted, perhaps the first field stars identified as such. However, since only 113 out of \LamostGiants stars

\end{itemize}
